### 2017-04-16 paper/oopsla17-submission/learning.tex
C for confidence score

\mysubsection{Labels}
\label{sec:labels}
Recall that we make predictions in two stages.
%
First, we use $\evalsym$ to predict for each subexpression whether it
should be blamed, and extract a confidence score $\mathcal{P}$ from the
$\Model$.
%
Thus, we define the output of the $\Model$ to be a boolean label, where
``false'' means the expression \emph{should not} change and ``true''
means the expression \emph{should} change.
%
This allows us to predict whether any individual expression should
change, but we would actually like to predict the \emph{most likely}
expressions to change.
%
Second, we \emph{rank} each subexpression by the confidence $\mathcal{P}$
that it should be blamed, and return to the user the top $k$
most likely blame assignments (in practice $k=3$).

>>>>

\mysubsection{Labels}
\label{sec:labels}
Recall that we make predictions in two stages.
%
First, we use $\evalsym$ to predict for each subexpression whether it
should be blamed, and extract a confidence score $\Runit$ from the
$\Model$.
%
Thus, we define the output of the $\Model$ to be a boolean label, where
``false'' means the expression \emph{should not} change and ``true''
means the expression \emph{should} change.
%
This allows us to predict whether any individual expression should
change, but we would actually like to predict the \emph{most likely}
expressions to change.
%
Second, we \emph{rank} each subexpression by the confidence $\Runit$
that it should be blamed, and return to the user the top $k$
most likely blame assignments (in practice $k=3$).
